\section*{Publications}

\begin{enumerate}[leftmargin=*, itemsep=1em]

\item
Victor, A.; Nhancololo, A.\,M.; Bah, H.\,A.\,F.; Xavier, S.\,P.; Gotine, A.\,R.\,M.\,E.; Moreira, V.\,A.; Charles, C.\,M.; Cerqueira-Silva, T.; Rondó, P.\,H.
\newblock National and regional temporal trends and forecasting of preterm birth in Brazil: Evidence from national Birth data (2014--2023) with projections to 2030.
\newblock \emph{BMC Pregnancy and Childbirth}, 2025. 
\newblock DOI: \href{https://doi.org/10.1186/s12884-025-08536-6}{10.1186/s12884-025-08536-6}

\item
Oliveira, W.\,A.; Scalon, J.\,D.; Nhancololo, A.\,M.
\newblock Characterization of the spatial distribution of \textit{Copaifera langsdorffii} and \textit{Xylopia brasiliensis} in an urban fragment of the Atlantic Forest domain.
\newblock \emph{Ciência Rural}, 2025. 
\newblock DOI: \href{https://doi.org/10.1590/0103-8478cr20240132}{10.1590/0103-8478cr20240132}

\item
Nhancololo, A.\,M.; Scalon, J.\,D.; Pereira, F.\,A.\,C.; Oliveira, W.\,A.; Silva, B.\,M.
\newblock Comparison between the laboratory method and the Stolf penetrometer in soil density analysis: a study using geostatistical methods.
\newblock \emph{SIGMAE}, vol.\,13, Jan.\ 2024.
\newblock DOI: \href{https://doi.org/10.29327/2520355.13.1-7}{10.29327/2520355.13.1-7}

\item
Nhancololo, A.\,M.; Cuinica, A.\,S.
\newblock Analysis of the Potential of Three-Dimensional Models in Teaching and Learning Spatial Geometry in 9th Grade: A Case Study of Chongoene Secondary School.
\newblock \emph{Kavenye Scientific Journal}, vol.\,1, pp.\,44--60, 2023. 
\newblock \href{https://www.researchgate.net/publication/378742882_Analysis_of_the_Potential_of_Using_Three-Dimensional_Models_in_the_Teaching_and_Learning_of_Solid_Geometry_in_the_9th_Grade_A_Case_Study_of_Chongoene_Secondary_School#fullTextFileContent}{[Link]}

\end{enumerate}

\vspace{1em}
\noindent\textbf{\Large Accepted Papers}

% O 'resume' continua a numeração da lista anterior
\begin{enumerate}[resume, leftmargin=*, itemsep=1em]

\item
Paludo, G.\,F.; Nhancololo, A.\,M.; Sousa Bueno Filho, J.
\newblock \textit{petioleFborder}: an R package with algorithms for automatic detection of petiole from the coordinates of leaf contour.
\newblock \emph{Plant Biosystems}, 2025. 
\newblock \href{https://drive.google.com/file/d/1_wETIYCp3Svumj2eTrHxBa-oYzlQvspl/view?usp=sharing}{[Link]}


\item
Damaceno, G.\,P.; Paludo, G.\,F.; Nhancololo, A.\,M.; Scalon, J.\,D.; Sabe, E.\,M.; da Silva, G.\,F.; Bueno-Filho, J.\,S.\,S.; da Silva, D.\,M.
\newblock Behavior of regression models for area data with outliers: an application to tuberculosis incidence.
\newblock \emph{Sigmae}, 2025. 
\newblock \href{https://drive.google.com/file/d/1Zkho4q2LNPxIskSow0zbESTl3Imu_75B/view?usp=sharing}{[PT paper Link]}

\end{enumerate}