\begin{longtable}[l]{@{}p{0.12\textwidth}p{0.88\textwidth}}

2025 & Nhancololo, A.\,M.; Alencar, A.\,P. ``The Dynamics of Insurgent Hotspots in Cabo Delgado, Mozambique: A Bayesian Spatio-Temporal Analysis (2017--2024)''. \emph{Presented on November 11, 2025, at the 6\textsuperscript{th} Graduate Meeting in Statistics at IME-USP}, São Paulo, Brazil. \href{https://drive.google.com/file/d/1njkjFxgrL-NGK5d-qCnuxhHohjaqDNXw/view?usp=sharing}{Link} \\[1.0em]

2025 & Nhancololo, A.\,M. ``Terrorism in Cabo Delgado, Mozambique: A spatio-temporal analysis of fatalities and their determinants (2017--2024) with forecasts to 2030.'' \emph{Presented on August 8, 2025, at the 69\textsuperscript{th} Brazilian Region of the International Biometric Society (RBras) and the 21\textsuperscript{st} Symposium on Statistics Applied to Agricultural Experimentation (SEAGRO)}, Vitória, Espírito Santo. \href{https://drive.google.com/file/d/1z71ZaLp6hSInL588_lLM9Pe_VjdPqvnc/view?usp=sharing}{Slides link} \\[1.0em]

2023 & Nhancololo, A.\,M.; Scalon, J.\,D. ``Textual Data Analysis Using Natural Language Processing (NLP) in R.'' (Seminar). \textbf{Online Access:} \href{https://drive.google.com/file/d/1iRTwmMuIIKOHb0XAlSCSPNt2x3AohBKm/view?usp=sharing}{Link} \\[0.5em]

2024 & Nhancololo, A.\,M.; \emph{et al.} ``Geostatistical Analysis of Soil Resistivity for Cassava Cultivation -- Lago Azul Farm in the Pontal do Paranapanema Region, São Paulo (SP).'' XXXIII Postgraduate Congress of UFLA (Conference). \href{https://drive.google.com/file/d/1cZyDKHRSTzG2U9cQZGi8riidFYjv6KEj/view?usp=sharing}{Link} \\[0.5em]

2024 & Nhancololo, A.\,M.; Scalon, J.\,D.; Oliveira, W.\,A.; Ossifo, M.\,E. ``Characterization of the Spatial Pattern of Fire Incidents in the Municipality of Lavras, MG.'' Brazilian Region of the International Biometric Society (RBras). \href{https://drive.google.com/file/d/1cZyDKHRSTzG2U9cQZGi8riidFYjv6KEj/view?usp=sharing}{Link} \\[0.5em]

2024 & Nhancololo, A.\,M.; Scalon, J.\,D.; Oliveira, W.\,A. ``Spatial Modeling of Point Processes Applied to Forest Ecology: A Case Study with \emph{Siparuna guianensis}.'' Brazilian Region of the International Biometric Society (RBras). \href{https://drive.google.com/drive/folders/1t6V0e8-OpA6rpamz9cq0cwsuhfdWOQN9?usp=sharing}{Poster link} \\[0.5em]

2023 & Nhancololo, A.\,M.; Scalon, J.\,D.; Oliveira, W.\,A. ``Estimation of Bivariate Models for Point Processes with Spatial Attraction in Native Species.'' XXXII Postgraduate Congress of UFLA. \href{https://drive.google.com/file/d/1cZyDKHRSTzG2U9cQZGi8riidFYjv6KEj/view?usp=sharing}{Link} \\[0.5em]

2021 & Nhancololo, A.\,M. ``Use of the Fundamental Principle of Counting in the Teaching and Learning Process of Combinatorial Analysis.'' UniSave Scientific Journeys. \href{https://drive.google.com/file/d/1cZyDKHRSTzG2U9cQZGi8riidFYjv6KEj/view?usp=sharing}{Link} \\[0.5em]

2020 & Nhancololo, A.\,M. ``Exploration of the Mathematical Knowledge Involved in the Activity of a Gravedigger.'' UniSave Scientific Journeys. \href{https://drive.google.com/file/d/1cZyDKHRSTzG2U9cQZGi8riidFYjv6KEj/view?usp=sharing}{Link} \\[0.5em]

2019 & Nhancololo, A.\,M. ``Teaching Linear Equation Systems through Problem Solving.'' UniSave Scientific Journeys. \href{https://drive.google.com/file/d/1cZyDKHRSTzG2U9cQZGi8riidFYjv6KEj/view?usp=sharing}{Link} \\

\end{longtable}