\begin{enumerate}[leftmargin=*, itemsep=1em]

\item
Nhancololo, A.\,M.; Alencar, A.\,P.; Paludo, G.\,F.; Zuniga, K.; Cuinica, A.\,S.; de Oliveira, W.\,A.; Damaceno, G.\,P.; Sabe, E.; Ferreira, V.; Lhone, M.\,A.; Scalon, J.\,D.
\newblock The Dynamics of Insurgent Hotspots in Cabo Delgado, Mozambique: A Bayesian Spatio-Temporal Analysis (2017--2024) with Forecasts to 2030.
\newblock \emph{Journal of the Royal Statistical Society: Series C}, 2025. \href{https://drive.google.com/file/d/1angafCARBJEO2lX9mzxQvX2ZocZ6ssjj/view?usp=sharing}{Link}

\item
Nhancololo, A.\,M.; Alencar, A.\,P.; Cuinica, A.\,S.; Paludo, G.\,F.; Damaceno, G.\,P.; Lhone, M.\,A.
\newblock Just-in-Time Repression: Modeling Police Violence Against Civilians in Mozambique (1997--2025) with Generalized Additive Models.
\newblock \emph{Sigmae}, 2025. \href{https://drive.google.com/file/d/1hdQ8QGeWTOXYossDN5P-loWQptxSeIlw/view?usp=sharing}{Link}

\item
Nhancololo, A.\,M.; Paludo, G.\,F.; Gianasi, F.\,M.; de Oliveira, W.\,A.
\newblock Spatial patterns of native tree species of an Atlantic Rainforest fragment and its association to edaphic variables. (\textbf{Based on the author's Master's thesis})
\newblock \emph{Iranian Journal of Science}, 2025.

\item
Paludo, G.\,F.; Nhancololo, A.\,M.; Mendes, A.\,M.; Cayo, A.\,C.; Huacani, R.\,C.; Damaceno, G.\,P.; Filho, J.\,S.\,B.
\newblock A memory game that explores variability.
\newblock \emph{Sigmae}, 2025. \href{https://drive.google.com/file/d/1jnrI3tmOf0Dw_NjbzosBq3pplcf6cAUd/view?usp=sharing}{Link}

\end{enumerate}